MCC Predictions

### 2018-06-19 stats/ex3_comparisons.Rmd
model comparisons update
updating model comparisons

```
```{r plot comparing models}

@@

@@

@@

allPriorProbs$priorProbs = list(
    c(0.0333333, 0.033333, 0.9666667), 
    c(0.9666667, 0.9666667, 0.0333333),
    c(0.3583333, 0.3583333, 0.6416667),
    c(0.6416667, 0.6416667, 0.3583333),
    c(0.1666667, 0.1666667, 0.8333333),
    c(0.8333333, 0.8333333, 0.1666667),
    c(0.4083333, 0.4083333, 0.5916667),
    c(0.5916667, 0.5916667, 0.4083333))
```

@@

  var loglike = sum(map(function(d){

  return modelPredictions.score(d.correct_inf)
    }, conditionSpecificData))

@@

   var loglike = sum(map(function(d){

  return priorOnlyPredictions.score(d.correct_inf)
    }, conditionSpecificData))

@@

  var loglike = sum(map(function(d){

  return noisyModelPredictions.score(d.correct_inf)
    }, conditionSpecificData))

@@

```{r model loglikelihoods}

llh.rsa <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
)%>%
  mutate(Model = "RSA")

llh.prior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000, chains = 3, cores = 3)
)%>%
  mutate(Model = "Prior only")

llh.rsa.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
)%>%
  mutate(Model = "RSA Noisy")

llh.prior.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
)%>%
  mutate(Model = "Prior only Noisy")

llh.prior.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
)%>%
  mutate(Model = "Prior only Regularized")

llh.rsa.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
)%>%
  mutate(Model = "RSA Regularized")

llh.rsa.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
)%>%
  mutate(Model = "RSA Noisy Regularized")

llh.prior.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 1e+5, chains = 3, cores = 3)
) %>%
  mutate(Model = "Prior only Noisy Regularized")

@@

likelihood_overview <- bind_rows(
  llh.rsa,
  llh.prior,
  llh.rsa.noise,
  llh.prior.noise,
  llh.prior.regPrior,
  llh.rsa.regPrior,
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)

@@

save.image(file="model.comparisons.RData")
```

>>>>

```{r plot comparing models}

@@

var two_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "circle", id:1, location: 2}
]

@@

```{r bda model prior, include = FALSE}
bdaModel.prior <-'
var allConditions = dataFromR.allConditions
var allData = dataFromR.allData
var allPriorProbs = dataFromR.allPriorProbs

var model = function(){
   var noise = 0

@@

allPriorProbs$priorProbs = list(
    c(0.0333333, 0.033333, 0.9666667), 
    c(0.9666667, 0.9666667, 0.0333333),
    c(0.3583333, 0.3583333, 0.6416667),
    c(0.6416667, 0.6416667, 0.3583333),
    c(0.1666667, 0.1666667, 0.8333333),
    c(0.8333333, 0.8333333, 0.1666667),
    c(0.4083333, 0.4083333, 0.5916667),
    c(0.5916667, 0.5916667, 0.4083333))

allPriorProbs2 <- allPriorProbs

allPriorProbs2$priorProbs = list(
    c(0.0333333, 0.9666667), 
    c(0.9666667, 0.0333333),
    c(0.3583333, 0.6416667),
    c(0.6416667, 0.3583333),
    c(0.1666667, 0.8333333),
    c(0.8333333, 0.1666667),
    c(0.4083333, 0.5916667),
    c(0.5916667, 0.4083333))

```{r predictions prior, include = FALSE}
bda0 <- webppl(
  program_code = paste(rsaUtils, rsaModel2, bdaModel.prior, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 6000, burn = 2000, verbose = T)
)

## distribution of model predictions
posterior.predictive1 = bda0 %>%
  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment"), sep="_")

prior.model <- posterior.predictive1 %>%
  mutate(Model="Prior Model",
         Adjustment = "Noise",
         Type = "Prior only")%>%
  group_by(Model,Adjustment,Type,Experiment,Change,Alignment) %>%
  summarise(mean = estimate_mode(value))

@@

var loglike = Binomial({
        p: Math.exp(modelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

@@

var loglike = Binomial({
        p: Math.exp(priorOnlyPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

@@

var loglike = Binomial({
        p: Math.exp(noisyModelPredictions.score(1)), 
        n: conditionSpecificData.length}).score(
      sum(_.map(conditionSpecificData, "correct_inf"))
    )

@@

```{r model loglikelihoods}
###################
# RSA Models
###################

llh.rsa <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA")

llh.rsa.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy")

llh.rsa.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Regularized")

llh.rsa.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, rsa.regularizedPrior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "RSA Noisy Regularized")

###################
# Prior only models
###################

llh.prior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only")

llh.prior.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.noise.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only Noisy")

llh.prior.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regPrior.loglikelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
)%>%
  mutate(Model = "Prior only Regularized")

llh.prior.noise.regPrior <- webppl(
  program_code = paste(rsaUtils, rsaModel2, prior.regularizedPrior.noise.likelihood, sep='\n'),
  data = list(allData = data, allConditions = allConditions, allPriorProbs = allPriorProbs), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "forward", samples = 5000),
  chains = 3, cores = 3
) %>%
  mutate(Model = "Prior only Noisy Regularized")

@@

likelihood_overview <- bind_rows(
  llh.rsa,
  llh.prior,
  llh.rsa.noise,
  llh.prior.noise,
  llh.prior.regPrior,
  llh.rsa.regPrior %>% filter(value != "-Infinity") %>% mutate(value = as.numeric(value)),
  llh.rsa.noise.regPrior,
  llh.prior.noise.regPrior)

@@

save.image(file="model.comparisons.RData")
